---
title: "Week05_Assignment_01"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

# Task 1: Analyzing Country-Level Statistics on Methane Emissions

## About the Data

## Cleaning the Data

```{r}
clean_up_wb_csv <- function(
    in_file_name,
    out_file_name) {
  
  # Read the raw World Bank CSV file, skipping the metadata rows
  wb_clean <- readr::read_csv(
    in_file_name,
    skip = 4,
    na = c("", ".."),
    show_col_types = FALSE
  )
  
  # Remove empty/unnamed columns created by the CSV import
  wb_clean <- wb_clean |>
    dplyr::select(-dplyr::starts_with("..."))
  
  # Rename the main columns so they are easier to use in R
  wb_clean <- wb_clean |>
    dplyr::rename(
      country_name = `Country Name`,
      country_code = `Country Code`,
      indicator_name = `Indicator Name`,
      indicator_code = `Indicator Code`
    )
  
  # Write the cleaned dataset to the output file
  readr::write_csv(
    wb_clean,
    out_file_name
  )
  
  # Return the cleaned dataset as well
  return(wb_clean)
}
```

```{r}
population <- clean_up_wb_csv(
  in_file_name = "data/world_bank_total_population/API_SP.POP.TOTL_DS2_en_csv_v2_267553.csv",
  out_file_name = "data/world_bank_total_population/population.csv"
)
```

## Importing the Data to RStudio

## Removing Rows not Pertaining to Countries

## Analyzing Country-Level Data

# Task 2: Activation Function Analysis

## Visualizing `swish()` Activation Function and its Gradient

## Toy Examples Calling `swish()` and `relu()`

## Exploring Other Activation Functions

# Task 3: Reflection on the Use of GenAI

```{r}

```

```{r}

```
